Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-03-22 fully-abstract-comp/technical-report.tex
more stuff

% Math packages
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{array}

@@

%%% Function arrows
\newcommand{\fun}{\rightarrow}

@@

% One argument
\newcommand{\sjmp}[1]{\oneinstr{\src{jmp}}{#1}}
\newcommand{\spush}[1]{\oneinstr{\src{push}}{#1}}
\newcommand{\spop}[1]{\oneinstr{\src{pop}}{#1}}
\newcommand{\ssload}[1]{\oneinstr{\src{sload}}{#1}}

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{isptr}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
\newcommand{\sgetl}[2]{\twoinstr{\src{getl}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\slea}[2]{\twoinstr{\src{lea}}{#1}{#2}}
\newcommand{\scall}[2]{\twoinstr{\src{call}}{#1}{#2}}

@@

% One argument
\newcommand{\tjmp}[1]{\oneinstr{\trg{jmp}}{#1}}

@@

%%% Domains
\newcommand{\plaindom}[1]{\mathrm{#1}}
\newcommand{\RegName}{\plaindom{RegisterName}}

\newcommand{\nats}{\mathbb{N}}

%%% Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\rn}{\var{rn}}
\newcommand{\stk}{\var{stk}}

@@

%%% Permissions
\newcommand{\plainperm}[1]{\mathrm{#1}}
\newcommand{\rwlxo}{\plainperm{rwlxo}}
\newcommand{\rwlo}{\plainperm{rwlo}}
\newcommand{\rwl}{\plainperm{rwl}}
\newcommand{\rwxo}{\plainperm{rwxo}}
\newcommand{\rwo}{\plainperm{rwo}}
\newcommand{\rw}{\plainperm{rw}}
\newcommand{\rxo}{\plainperm{rxo}}
\newcommand{\ro}{\plainperm{ro}}
\newcommand{\readonly}{\plainperm{r}}
\newcommand{\noperm}{\plainperm{0}}
\newcommand{\nopermo}{\plainperm{0o}}
\newcommand{\enter}{\plainperm{e}}

@@

%%% Functions

\begin{document}
\section{The two capability machines}
\subsection{Domains}
\[
  \begin{array}{rcl}
    \{\pcreg,\rO,\rstk \} & \subseteq & \RegName
  \end{array}
\]

\subsection{Syntax}
The target machine is a simple capability machine with memory capabilities, local capabilities and enter capabilities. The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \RegName  \src{\setminus \{\rO,\rstk\}}\\
\trg{\rn} &::= &  \trg{r} \mid n \\
\trg{i} &::= & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetl{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tlea{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \\
      & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}}
\end{array}
\]
Where the \sourcecolortext{} only applies for the source language which we define below.

The source machine is also a capability machine with memory capabilities, local capabilities and enter capabilities. Unlike the target machine, the source machine is going to have a built in stack. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \RegName \setminus \{\rO,\rstk\}\\
    \src{\rn} &::= & \src{r} \mid n \\
    \src{i} & ::= &  \trg{i} \mid \spop{\src{r}} \mid \spush{\src{\rn}} \mid \ssload{\src{\rn}} \mid \scall{\src{r}}{\src{\rn}} \mid \sreturn
  \end{array}
\]
There are two syntactic differences between the source language and the target language: (1) The source language does not permit register names $\rO$ and $\rstk$ to be used because they will play a special role in the compilation scheme. (2) The source language has explicit call/return instructions as well as the stack manipulation instructions $\spop{}$, $\spush{}$, $\ssload{}$, and $\scall{}{}$. We will define the semantic of these below.

\subsection{Permissions}

\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (7) {$\rwlxo$};
    \node[main node] (1) [below of=7] {$\rwxo$};
    \node[main node] (2) [below of=1] {$\rxo$};
    \node[main node] (3) [below of=2] {$\enter$};

    \node[main node] (9) [below left of=7] {$\rwlo$};
    \node[main node] (10) [below of=9] {$\rwo$};
    \node[main node] (11) [below of=10] {$\ro$};
    \node[main node] (12) [below of=11] {$\nopermo$};

    \node[main node] (8) [above left of=9] {$\rwl$};
    \node[main node] (4) [below of=8] {$\rw$};
    \node[main node] (5) [below of=4] {$\readonly$};
    \node[main node] (6) [below of=5] {$\noperm$};

    \path[every node/.style={font=\sffamily\small}]
    (7) edge (1)
    (8) edge (4)
    (1) edge (2)
    (2) edge (3)
    (4) edge (5)
    (5) edge (6)

    (9) edge (10)
    (10) edge (11)
    (11) edge (12)

    (9) edge (7)
    (10) edge (1)
    (11) edge (2)
    (12) edge (3)

    (9) edge (8)
    (10) edge (4)
    (11) edge (5)
    (12) edge (6);
  \end{tikzpicture}

@@

\subsection{Compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\clearpage
\section{Examples}
\subsection{Capability opacity}
The following pseudo program demonstrates the need of opaque capabilities. If we assume a system with no opaque capabilities, then the following programs break compiler correctness
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
p1 ::= if r1 is length 2 then
         call r1 with the following callback in r5:
           {put $\textit{\texttt{diverging}}$ closure in r2;
            return};
         halt
       else diverge

>>>>

% Math packages
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{array}
\usepackage{stmaryrd}

@@

%%% Comments
% Comments
\newcommand\lau[1]{{\color{purple} \sf \footnotesize {LS: #1}}\\}
\newcommand\dominique[1]{{\color{purple} \sf \footnotesize {DD: #1}}\\}
\newcommand\lars[1]{{\color{purple} \sf \footnotesize {LB: #1}}\\}

%%% Math notation
\newcommand{\defeq}{\stackrel{\textit{\tiny{def}}}{=}}
\newcommand{\defbnf}{::=}
\newcommand{\sem}[1]{\left\llbracket #1 \right\rrbracket}
\newcommand{\ssem}[2][\Phi]{\sem{#2}_{\mathrm{src}}(#1)}

% Function arrows
\newcommand{\fun}{\rightarrow}
\newcommand{\parfun}{\rightharpoonup}

@@

% One argument
\newcommand{\sjmp}[1]{\oneinstr{\src{jmp}}{#1}}
\newcommand{\ssetatob}[1]{\oneinstr{\src{seta2b}}{#1}}
\newcommand{\spush}[1]{\oneinstr{\src{push}}{#1}}
\newcommand{\spop}[1]{\oneinstr{\src{pop}}{#1}}

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{isptr}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
\newcommand{\sgetl}[2]{\twoinstr{\src{getl}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\slea}[2]{\twoinstr{\src{lea}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\scall}[2]{\twoinstr{\src{call}}{#1}{#2}}

@@

% One argument
\newcommand{\tjmp}[1]{\oneinstr{\trg{jmp}}{#1}}
\newcommand{\tsetatob}[1]{\oneinstr{\trg{seta2b}}{#1}}

@@

%%% Domains
\newcommand{\plaindom}[1]{\mathrm{#1}}

\newcommand{\nats}{\mathbb{N}}
\newcommand{\ints}{\mathbb{Z}}

%%% Updates
\newcommand{\update}[2]{[#1 \mapsto #2]}
\newcommand{\updReg}[3][\Phi]{#1\update{\sreg.#2}{#3}}
\newcommand{\updPc}[2][\Phi]{\updReg[#1]{\pcreg}{#2}}

%%% Source dom
\newcommand{\sourcedom}[1]{\mathrm{#1}}
\newcommand{\sRegName}{\sourcedom{RegisterName}}
\newcommand{\sAddr}{\sourcedom{Addr}}
\newcommand{\sPerm}{\sourcedom{Perm}}
\newcommand{\sCap}{\sourcedom{Cap}}
\newcommand{\sWord}{\sourcedom{Word}}
\newcommand{\sMem}{\sourcedom{Memory}}
\newcommand{\sReg}{\sourcedom{RegisterFile}}
\newcommand{\sStk}{\sourcedom{Stack}}
\newcommand{\sConf}{\sourcedom{Conf}}
\newcommand{\sExecConf}{\sourcedom{ExecConf}}
\newcommand{\sGlobal}{\sourcedom{Global}}
\newcommand{\sMemSeg}{\sourcedom{MemorySegment}}
\newcommand{\sStkFrame}{\sourcedom{StackFrame}}
\newcommand{\sStack}{\sourcedom{Stack}}

\newcommand{\smem}{\sourcedom{mem}}
\newcommand{\sreg}{\sourcedom{reg}}
\newcommand{\sstk}{\sourcedom{stk}}
\newcommand{\smsstk}{\sourcedom{ms_{stk}}}
\newcommand{\sstkframe}{\sourcedom{frame}}
\newcommand{\sopc}{\sourcedom{opc}}
\newcommand{\sastk}{\sourcedom{a_{stk}}}
\newcommand{\sperm}{\sourcedom{perm}}
\newcommand{\sgl}{\sourcedom{g}}
\newcommand{\sbase}{\sourcedom{base}}
\newcommand{\send}{\sourcedom{end}}
\newcommand{\saddr}{\sourcedom{a}}
\newcommand{\scap}{\sourcedom{c}}
\newcommand{\sms}{\sourcedom{ms}}

\newcommand{\stkptr}[4]{\sourcedom{stack\text{-}ptr}(#1,#2,#3,#4)}
\newcommand{\retptr}{\sourcedom{ret\text{-}ptr}}

\newcommand{\failed}{\mathrm{failed}}
\newcommand{\halted}{\mathrm{halted}}

%%% Target domain
\newcommand{\targetdom}[1]{\mathrm{#1}}
\newcommand{\tRegName}{\targetdom{RegisterName}}

%%% Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\rn}{\var{rn}}
\newcommand{\reg}{\var{reg}}
\newcommand{\mem}{\var{mem}}
\newcommand{\ms}{\var{ms}}
\newcommand{\pc}{\var{pc}}
\newcommand{\stk}{\var{stk}}
\newcommand{\opc}{\var{opc}}

@@

%%% locality
\newcommand{\plainlocality}[1]{\mathrm{#1}}
\newcommand{\glob}{\plainlocality{global}}
\newcommand{\local}{\plainlocality{local}}

%%% Permissions
\newcommand{\plainperm}[1]{\mathrm{#1}}
\newcommand{\rwlx}{\plainperm{rwlx}}
\newcommand{\rwx}{\plainperm{rwx}}
\newcommand{\rx}{\plainperm{rx}}
\newcommand{\rwlxo}{\plainperm{rwlxo}}
\newcommand{\rwlo}{\plainperm{rwlo}}
\newcommand{\rwl}{\plainperm{rwl}}
\newcommand{\rwxo}{\plainperm{rwxo}}
\newcommand{\rwo}{\plainperm{rwo}}
\newcommand{\rw}{\plainperm{rw}}
\newcommand{\rxo}{\plainperm{rxo}}
\newcommand{\ro}{\plainperm{ro}}
\newcommand{\readonly}{\plainperm{r}}
\newcommand{\noperm}{\plainperm{0}}
\newcommand{\nopermo}{\plainperm{0o}}
\newcommand{\enter}{\plainperm{e}}
\newcommand{\entero}{\plainperm{eo}}

@@

%%% Functions
\newcommand{\plainfun}[2]{
  \ifthenelse{\equal{#2}{}}
  {\mathit{#1}}
  {\mathit{#1}(#2)}
}
\newcommand{\updPcAddr}[1]{\plainfun{updatePc}{#1}}
\newcommand{\updPcPerm}[1]{\plainfun{updatePcPerm}{#1}}
\newcommand{\clearms}[1]{\plainfun{clear_{ms}}{#1}}
\newcommand{\clearlocreg}[1]{\plainfun{clear_{loc,reg}}{#1}}

\begin{document}
\section{TODO}
\begin{itemize}
\item Linking
\item Component
\item Cross-language LR
\end{itemize}

\section{The two capability machines}
\subsection{Domains}
Source language domains:
\[
  \begin{array}{rrcl}
   \saddr,\sbase \in & \sAddr & \defeq & \nats \\
    &\sWord & \defeq & \ints \uplus \sCap\\
   \sperm \in& \sPerm & \defbnf & \dots \\
    \sgl \in&\sGlobal & \defbnf & \glob \mid \local \\
    &\sCap &::= & \left\{((\sperm,\sgl),\sbase,\send,\saddr) \mid \send \in \sAddr \cup \{\infty\}\right\} {\sourcecolor{} \uplus}\\
    & & & {\sourcecolor{} \{ \stkptr{\sperm}{\sbase}{\send}{\saddr} \}\uplus}\\ 
    & & & {\sourcecolor{} \{ \retptr \}}\\ 
    &\sRegName & \defbnf &\pcreg \mid \rO \mid \rstk \mid \dots \\
    &\sReg & \defeq & \sRegName \fun \sWord\\
    & \sMem & \defeq & \sAddr \fun \sWord \\
    & \sMemSeg & \defeq & \sAddr \parfun \sWord \\
    {\sourcecolor{} \sstkframe \in} & {\sourcecolor{} \sStkFrame} & {\sourcecolor{} \defeq} & {\sourcecolor{} \sCap \times \sMemSeg \times \sAddr}\\
    {\sourcecolor{} \sstk \in}& {\sourcecolor{} \sStack} & {\sourcecolor{} \defeq} & {\sourcecolor{} \sStkFrame^*} \\
    \Phi \in & \sExecConf & \defeq & \sMem \times \sReg {\sourcecolor{} \; \times \; \sStack \times \sMemSeg }\\
    &\sConf & \defeq & \sExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \sMem)
  \end{array}
\]
The target language domains are all the non blue parts in the above.

More convenient definitions
\[
  \begin{array}{rcl}
    \Phi(r) & \defeq & \Phi.\sreg(r)
  \end{array}
\]
where $r\in \sRegName$

\subsection{Syntax}
The target machine is[dashed] a simple capability machine with memory capabilities, local capabilities and enter capabilities. The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &::= &  \trg{r} \mid n \\
\trg{i} &::= & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetl{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tlea{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \\
      & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}
\end{array}
\]

The source machine is also a capability machine with memory capabilities, local capabilities and enter capabilities. Unlike the target machine, the source machine is going to have a built in stack. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \sRegName \setminus \{\rO,\rstk\}\\
    \src{\rn} &::= & \src{r} \mid n \\
    \src{i} & ::= &  \trg{i} \mid \scall{\src{r}}{\src{\rn}}
  \end{array}
\]
There is one suntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{}{}$ instruction.
\subsection{Permissions}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwlx) {$\rwlx$};
    \node[main node] (rwx) [below of=rwlx] {$\rwx$};
    \node[main node] (rx) [below of=rwx] {$\rx$};
    \node[main node] (e) [below of=rx] {$\enter$};

    \node[main node] (rwlxo) [below right of=rwlx,yshift=-0.1cm] {$\rwlxo$};
    \node[main node] (rwxo) [below of=rwlxo] {$\rwxo$};
    \node[main node] (rxo) [below of=rwxo] {$\rxo$};
    \node[main node] (eo) [below of=rxo] {$\entero$};

    \node[main node] (rwl) [below left of=rwlx,xshift=-0.5cm,yshift=-0.3cm] {$\rwl$};
    \node[main node] (rw) [below of=rwl] {$\rw$};
    \node[main node] (r) [below of=rw] {$\readonly$};
    \node[main node] (0) [below of=r] {$\noperm$};

    \node[main node] (rwlo) [below right of=rwl,yshift=-0.1cm] {$\rwlo$};
    \node[main node] (rwo) [below of=rwlo] {$\rwo$};
    \node[main node] (ro) [below of=rwo] {$\ro$};
    \node[main node] (0o) [below of=ro] {$\nopermo$};

    \path[every node/.style={font=\sffamily\small}]
    (rwlxo) edge (rwxo)
    (rwxo) edge (rxo)
    (rxo) edge (eo)

    (rwl) edge (rw)
    (rw) edge (r)
    (r) edge (0)

    (rwlo) edge (rwo)
    (rwo) edge (ro)
    (ro) edge (0o)

    (rwlx) edge[dashed] (rwx)
    (rwx) edge[dashed] (rx)
    (rx) edge[dashed] (e)

    (rwlo) edge (rwlxo)
    (rwo) edge (rwxo)
    (ro) edge (rxo)
    (0o) edge (eo)

    (rwlo) edge (rwl)
    (rwo) edge (rw)
    (ro) edge (r)
    (0o) edge (0)

    (rwl) edge (rwlx)
    (rw) edge[dashed] (rwx)
    (r) edge[dashed] (rx)
    (0) edge[dashed] (e)

    (rwlxo) edge (rwlx)
    (rwxo) edge[dashed] (rwx)
    (rxo) edge[dashed] (rx)
    (eo) edge[dashed] (e);
  \end{tikzpicture}

@@

\subsection{Operational Semantics}
\subsubsection{Notes}
Genrally:
\begin{itemize}
\item Opaque capabilities: Only allow locality and permission to be inspected (i.e., no addresses disclosed).
\end{itemize}

Source language:
\begin{itemize}
\item No jumps to enter (call reserved for this)
\item Variable length instructions that match the length of the compiled instructions
  \begin{itemize}
  \item Opaque capabilities do not hide the length of a program (especially an issue if we ever hope to have error recovery).
  \item This is needed for correctness. See subsection~\ref{subsec:capability-opacity} for an example it helps prevent.
  \end{itemize}
\end{itemize}

Target language:
\begin{itemize}
\item 
\end{itemize}

\subsubsection{Helpful functions}
\[
  \updPcAddr \defeq \dots
\]

\[
  \updPcPerm \defeq \dots
\]

\[
  \clearms \defeq \dots
\]

\[
  \clearlocreg \defeq \dots
\]

\subsubsection{Source Language}

\begin{align*}
  \ssem{\sjmp{r}} = & 
    \begin{cases}
      \Phi
      \begin{aligned}[t]
        & \update{\sreg.\pcreg}{\opc} \\
        & \update{\smsstk}{\ms_\stk' \uplus \clearms{\ms_\stk}}\\
        & \update{\sastk}{a_\stk'}\\
        & \update{\sstk}{\stk'}
      \end{aligned} & \Phi(r) = \retptr \text{ and }
      \Phi.\sstk = (\opc,\ms_\stk',a_\stk') :: \stk'\\
      & \\
      \updPc{\updPcPerm{\Phi(r)}} & \text{otherwise}
    \end{cases} \\
\end{align*}
\begin{align*}
  \ssem{\scall{r}{\rn}} = & 
    \begin{cases}
      (\mem,\reg',\stk',\ms_\stk') & \Phi = (\mem,\reg,\stk,\ms_\stk) \text{ and }\\
      \\
      \failed & \text{otherwise}
    \end{cases}
\end{align*}

\subsubsection{Target Language}

\subsection{Compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\clearpage
\section{Examples}
\subsection{Capability Opacity}
\label{subsec:capability-opacity}
This example was introduced when we envisioned a capability machine with $\spush{}$, $\spop{}$, $\ssload{}{}$, $\scall{}{}$ and $\sreturn$ instructions. The below example is a motivation for having variable length instructions in the source language because if we have enough memory to ``do the same'' in the target language as in the source language, then the below example does not work.

The following pseudo program demonstrates the need of opaque capabilities. If we assume a system with no opaque capabilities, then the following programs break compiler correctness
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
p1 ::= if r1 is length 2 then
         call r1 with the following callback in r5:
           {put $\textit{\texttt{diverging}}$ closure in r2;
            return};
         halt
       else diverge
